Relationships in the extremes and their influence on competition and coexistence

### 2021-09-30 paper/Paper.Rnw
added acknowledgement

The authors thank Shyamolina Ghosh for initially suggesting the research problem, and Lawrence Sheppard, Max Castorani,
Jon Walter, Jude Kastens, Vadim Karatayev, Emily Arsenault, Steve Ellner, and Robin Snyder for helpful discussions. 
The authors were partly supported by US National
Science Foundation grants 1714195 and 2023474, the James S McDonnell Foundation, and the California Department of Fish and
Wildlife Delta Science Program. 
%***DAN: Jasmim, please add any other acknolwedgments here - anyone else you have discussed this with or anything like that.
%Be generous here, add people even if they only helped a tiny bit. If Steve consents to be coauthor, we take him
%off this list and add him to the author list.

>>>>

The authors thank Shyamolina Ghosh for initially suggesting the research problem, and Lawrence Sheppard, Max Castorani,
Jon Walter, Jude Kastens, Vadim Karatayev, Emily Arsenault, Neil Thimmesch, Steve Ellner, and Robin Snyder for helpful discussions. 
The authors were partly supported by US National
Science Foundation grants 1714195 and 2023474, the James S McDonnell Foundation, and the California Department of Fish and
Wildlife Delta Science Program. 
%***DAN: Jasmim, please add any other acknolwedgments here - anyone else you have discussed this with or anything like that.
%Be generous here, add people even if they only helped a tiny bit. If Steve consents to be coauthor, we take him
%off this list and add him to the author list.
